Deriving Multi-Headed Planar Dependency Parses from Link Grammar Parses

### 2014-12-10 doc/slides/hong+eisner.TLT13.slides.tex
updated slides. Added link analysis table from the appendix (I had to cut it down). Added the stability-of-results graph.
cleaned up/improved the summarizing statistics slide.

\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

\frame{\frametitle{Link Grammars}
  \begin{itemize}
    \item[] Grammar-based formalism for projective dependency parsing with undirected links
    %\item We set out to discover if the undirected links are actually directed relationships.
  \end{itemize}
}

\frame{\frametitle{Link Grammars: Example Parse}
\begin{figure}
  \begin{dependency}[edge style={-}]
	\begin{deptext}
	  - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	  the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	\end{deptext}
	\depedge[edge above, thick, edge style = {red}]{2}{3}{S}
	\depedge[edge above, thick, edge style = {red}]{3}{6}{I}
	\depedge[edge above, thick, edge style = {red}]{2}{1}{D}
	\depedge[edge above, thick, edge style = {red}]{7}{8}{MV}
	\depedge[edge above, thick, edge style = {red}]{6}{7}{P}
	\depedge[edge above, thick, edge style = {red}]{8}{9}{J}
	\deproot[edge above, thick, edge style = {red}]{2}{W}
	\deproot[edge above, thick, edge style = {red}]{7}{WV}
	\deproot[edge above, thick, edge style = {red}]{10}{X}
	\depedge[edge above, thick, edge style = {red}]{6}{4}{E}
	\depedge[edge above, thick, edge style = {red}]{6}{5}{E}
  \end{dependency}
  \caption*{Link Parse of a sentence from Penn Tree Bank}
\end{figure}

@@

\frame{\frametitle{Data Sets}
%\begin{itemize}
%  \item[] 18,577 English sentences with 10,960 connected parses
%  \item[] 18,577 unlabeled Russian sentences with 4,913 connected parses
%\end{itemize}
  \begin{table}[h]
    \begin{tabular}{|l|l|l|}
      \hline
      & \# Sentences & \# Connected Parses \\ \hline
      English             & 18,577        & 10,960               \\ \hline
      Russian (unlabeled) & 18,577        & 4,913                \\ \hline
    \end{tabular}
  \end{table}

  On the English data set:

  \begin{itemize}
  \item[] Link Data has 8\% additional edges over the CoNLL.
  \item[] 52\% of links match CoNLL arcs
  \item[] 57\% of CoNLL arcs match links
  \end{itemize}

  \NoteJH{I skipped the ``Stability of Results'' section}
}

@@

\frame{\frametitle{ILP Results}
%  \begin{table}[h]
%    \begin{tabular}{|l|l||l|}
%      \hline
%      & & out of total \\ \hline
%      Link types & & \\allowing both directions & 7 & 113 \\ \hline
%      Link tokens & & \\requiring disallowed direction & & \\via slack & 4043 & 195,000 \\ \hline
%    \end{tabular}
%  \end{table}
  \begin{itemize}
    \item[] Link types that allowed both directions:
      \begin{itemize}
        \item[] 7 / 113 = 6.19\%
      \end{itemize}
    \item[] Link tokens that required disallowed direction via slack:
      \begin{itemize}
      \item[] 4043 / 195,000 = 2.07\%
      \end{itemize}
  \end{itemize}
  \begin{itemize}
    \uncover<1>{\item[]}
    \uncover<2->{\item[] The link labels mostly have a consistent direction.}
  \end{itemize}
}

@@

\NoteJH{Should I include a section of the appendix table? Which rows should I include?}
}

>>>>

\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{longtable}

@@

\frame{\frametitle{Link Grammars}
  \begin{itemize}
    \item[] Grammar-based formalism for projective dependency parsing with undirected links
  \end{itemize}
}

\frame{\frametitle{Link Grammars: Example Parse}
  \begin{figure}
    \begin{dependency}[edge style={-}]
	  \begin{deptext}
	    - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	    the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	  \end{deptext}
	  \depedge[edge above, thick, edge style = {red}]{2}{3}{S}
	  \depedge[edge above, thick, edge style = {red}]{3}{6}{I}
	  \depedge[edge above, thick, edge style = {red}]{2}{1}{D}
	  \depedge[edge above, thick, edge style = {red}]{7}{8}{MV}
	  \depedge[edge above, thick, edge style = {red}]{6}{7}{P}
	  \depedge[edge above, thick, edge style = {red}]{8}{9}{J}
	  \deproot[edge above, thick, edge style = {red}]{2}{W}
	  \deproot[edge above, thick, edge style = {red}]{7}{WV}
	  \deproot[edge above, thick, edge style = {red}]{10}{X}
	  \depedge[edge above, thick, edge style = {red}]{6}{4}{E}
	  \depedge[edge above, thick, edge style = {red}]{6}{5}{E}
    \end{dependency}
    \caption*{Link Parse of a sentence from Penn Tree Bank}
  \end{figure}
}

@@

\frame{\frametitle{Data Sets}
%\begin{itemize}
%  \item[] 18,577 English sentences with 10,960 connected parses
%  \item[] 18,577 unlabeled Russian sentences with 4,913 connected parses
%\end{itemize}

  Data Sets taken from:
  \begin{itemize}
    \item[] CoNLL 2007 Shared Task (English)
    \item[] ACL 2013 Shared Task of Machine Translation (Russian)
  \end{itemize}

  \begin{figure}[h]
    \centering
    \begin{tabular}{|l|l|l|}
      \hline
       & Input Sentences & Output Connected Parses \\ \hline
       English  & 18,577        & 10,960               \\ \hline
       Russian & 18,577        & 4,913                \\ \hline
    \end{tabular}
  \end{figure}
}

\frame{\frametitle{Stability of Results}
  \begin{figure}
    \centering
    \includegraphics[width=0.7\linewidth]{precision_recall}
  \end{figure}
}

@@

\frame{\frametitle{On the English Data Set:}

  \uncover<2->{Multiheadedness}
  \begin{itemize}
  \uncover<2->{\item[] Link Data has 8\% additional edges over the CoNLL.}
  \end{itemize}

  \uncover<3->{CoNLL Matches}
  \begin{itemize}
  \uncover<3->{\item[] 52\% of links match CoNLL arcs
  \item[] 57\% of CoNLL arcs match links}
  \end{itemize}

  \uncover<4->{Directionality}%\uncover<5->{ is Mostly Consistent!}
  \begin{itemize}
  \uncover<4->{\item[] 6.19\% of link types allowed both directions %($\frac{7}{113}$)
  \item[] 2.07\% of link tokens required disallowed direction via slack %($\frac{4043}{195,000}$)
  }
  \end{itemize}

  %\uncover<4->{The link labels mostly have a consistent direction.}
  %\uncover<5->{\item[] The direction is often the same as CoNLL when there is a corresponding arc}

\frame{\frametitle{ILP Results: Top 25 Most Occuring Labels}

  \begin{figure}
    \centering
    \input{link_table_filtered.tex}
  \end{figure}
}

%\frame{\frametitle{ILP Results: Top 25 Most Occuring Labels}
%  \input{link_table_filtered_part2.tex}
%}

@@
